R tools for accessing research literature for text mining

### 2019-08-23 manuscript.tex
fix #20 move case studies further up

@@

@@

\hypertarget{how-to-text-mine-from-r-three-case-studies}{%
\section{How to text mine from R: Three case
studies}\label{how-to-text-mine-from-r-three-case-studies}}

>>>>

\hypertarget{text-mining-in-r-three-case-studies}{%
\section{Text mining in R: Three case
studies}\label{text-mining-in-r-three-case-studies}}

@@

\hypertarget{learn-more}{%
\subsection{Learn more}\label{learn-more}}

To learn how to use the above packages, follow the links to get to
documentation, and how to report issues. The rOpenSci forum
(\url{https://discuss.ropensci.org/}) is a good place to ask questions
about these packages.

@@
